Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
fixed lowercase

- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
- Pollster: Represents the name of the polling organization that conducted the poll. 
- Candidate: The name of the candidate in the poll
- Sample Size (sample_size): size of the respondents participating in the poll
- State (state): the state of the poll was taken in 
- End_date: the day the poll ended
- Start_date: the day the poll started

@@

\includepdf[pages=-]{../other/Survey/Survey.pdf}

>>>>

- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
- Pollster: Represents the name of the polling organization that conducted the poll. 
- Candidate: The name of the candidate in the poll
- Sample Size (sample_size): size of the respondents participating in the poll
- State (state): the state of the poll was taken in 
- End_date: the day the poll ended

@@

\includepdf[pages=-]{../other/survey/survey.pdf}
